%!TEX root = ../../../2019main.tex
\vspace{10pt}
\subsubsection*{\bf Physical Environment Monitors}
\vspace{3pt}
\noindent {\sf [Spokesperson :\ Takaaki YOKOZAWA ]}

\vspace{3pt}
\noindent {\sf \small ICRR, The Univ.\ of Tokyo, Hida, Gifu 506-1205}

\vspace{3pt}

Because the amplitude of gravitational waves(GWs) are very small, 
we must take care everything which can be a noise source.
One of the major noise sources is environmental disturbance through earthquakes, 
effects from magnetic and acoustic fields, temperature and so on.
To investigate the effect from the environmental noise, 
we installed various types of the monitors, which are called as
physical environmental monitors (PEMs).
Also, because KAGRA interferometer was developed in the underground environment and 
operated with cryogenic temperature (20K).
Those environment and technique is essential to the next generation
GW interferometer. 
So the understanding of the KAGRA interferometer environment is  key technology.

Six seismometers were installed to evaluate the ground motion in the
underground environment and those seismometer were also used for the suspension 
control to reduce the mirror motion.
the accelerometers and microphones were also installed to monitor the optical tables.
Such auxiliary optics on the optical tables were used for many purpose, such as 
laser source stabilization, mode matching, sensing for the interferometer control and 
controls of the photon calibrator.
Those PEMs were used for evaluating not only the stationary interferometer noise but also
narrow band frequency noise and transient noise identification.

The temperature monitor is also important for keep the suspensions healthy.
If the temperature changed 1 degree, the height of the mirror motion was changed and 
it became difficult to keep the interferometer condition.
For monitoring the temperature, we installed total 77 thermometer, which can monitor both
temperature and humidity and made the web site to monitor the temperature drift.

Finally, to evaluate the effect from the environments, we established the system of the 
environmental injection, such as acoustic injection and magnetic injection system.
By performing the acoustic injection, we turned out that the peaks of the 160, 280 and 
360 Hz came from the acoustic environmental noise.
