%!TEX root = ../../../2019main.tex

\begin{thebibliography}{9}

\bibitem{kagra_review} "KAGRA: 2.5 generation interferometric gravitational wave detector",
KAGRA collaboration, Nature Astronomy, Vol. 3, January 2019, 35-40

\bibitem{ikagra_paper} "Construction of KAGRA: an underground gravitational-wave observatory",
KAGRA collaboration,
Prog. Theor. Exp. Phys. 2018, 013F01 (2018)

\bibitem{phase1_paper} "First cryogenic test operation of underground km-scale gravitational-wave observatory KAGRA",
KAGRA collaboration, Class. Quantum Grav. 36 165008 (2019)


\bibitem{scenario_paper} "Prospects for observing and localizing gravitational-wave transients with Advanced LIGO, Advanced Virgo and KAGRA",
Abbott, B.P., Abbott, R., Abbott, T.D. et al. arXiv:1304.0670v10 [gr-qc]

\bibitem{o3_suspend} https://www.ligo.caltech.edu/news/ligo20200326

\bibitem{moa} https://gwdoc.icrr.u-tokyo.ac.jp/cgi-bin/DocDB/ShowDocument?docid=10663
\bibitem{moa_at} https://gwdoc.icrr.u-tokyo.ac.jp/cgi-bin/DocDB/ShowDocument?docid=10664
\bibitem{loi_o3} https://gwdoc.icrr.u-tokyo.ac.jp/cgi-bin/DocDB/ShowDocument?docid=10813

%2019
\bibitem{quantum} "Quantum noise reduction techniques in KAGRA", K Somiya, The European Physical Journal D volume 74, Article number: 10 (2020)
\bibitem{als} "An arm length stabilization system for KAGRA and future gravitational-wave detectors", T Akutsu et al., Class. Quantum Grav. 37 (2020) 035004 (19pp)

\bibitem{damping} "Vibration isolation system with a compact damping system for power recycling mirrors of KAGRA", Y Akiyama et al., Class. Quantum Grav. 36 (2019) 095015 (16pp)
\bibitem{cryo-op} "First cryogenic test operation of underground km-scale gravitational-wave observatory KAGRA", T Akutsu et al., Class. Quantum Grav. 36 (2019) 165008 (22pp)
\bibitem{mzm} "Design and experimental demonstration of a laser modulation system for future gravitational-wave detectors", K Yamamoto et al., Class. Quantum Grav. 36 (2019) 205009 (19pp)

\bibitem{contami} "Molecular adsorbed layer formation on cooled mirrors and its impacts on cryogenic gravitational wave telescopes", K Hasegawa et al., Phys. Rev. D 99, 022003
\bibitem{sapphire mirror} "Influence of nonuniformity in sapphire substrates for a gravitational wave telescope", K Somiya et al., Phys. Rev. D 100, 082005
%\bibitem{tilt} "Demonstration for a two-axis interferometric tilt sensor in KAGRA", Keiko Kokeyama,  Phys. Lett. A 382 (2018) 1950\UTF{2013}1955
%\bibitem{localizing} "Prospects for observing and localizing gravitational-wave transients with Advanced LIGO, Advanced Virgo and KAGRA", B. P. Abbott et al., Living Reviews in Relativity volume 21, Article number: 3 (2018) 

\bibitem{kagra status} "The status of KAGRA underground cryogenic gravitational wave telescope", T Akutsu et al., Journal of Physics: Conference Series, Volume 1342, XV International Conference on Topics in Astroparticle and Underground Physics 24-28 June 2017, Sudbury, ON, Canada
%2019



%
%
%
%\bibitem{xarm_com} "An arm length stabilization system for KAGRA and future gravitational-wave detectors",
%KAGRA collaboration,
%to be published in Class. Quantum Grav. (2019)



%
%\bibitem{michimura} "Mirror actuation design for the interferometer control of the KAGRA gravitational wave telescope",
%Yuta Michimura, Tomofumi Shimoda, Takahiro Miyamoto, Ayaka Shoda, Koki Okutomi, Yoshinori Fujii, Hiroki Tanaka, Mark A. Barton, Ryutaro Takahashi, Yoichi Aso, Tomotada Akutsu, Masaki Ando, Yutaro Enomoto, Raffaele Flaminio, Kazuhiro Hayama, Eiichi Hirose, Yuki Inoue, Takaaki Kajita, Masahiro Kamiizumi, Seiji Kawamura, Keiko Kokeyama, Kentaro Komori, Rahul Kumar, Osamu Miyakawa, Koji Nagano, Masayuki Nakano, Naoko Ohishi, Ching Pin Ooi, Fabian Erasmo Pena Arellano, Yoshio Saito, Katsuhiko Shimode, Kentaro Somiya, Hiroki Takeda, Takayuki Tomaru, Takashi Uchiyama, Takafumi Ushiba, Kazuhiro Yamamoto, Takaaki Yokozawa, Hirotaka Yuzurihara, Classical and Quantum Gravity 34, 225001(2017)
%
%\bibitem{gif} "Design and operation of a 1500-m laser strainmeter installed at underground site in Kamioka",
%Akito Araya, Akiteru Takamori, Wataru Morii, Kouseki Miyo, Masatake Ohashi, Kazuhiro Hayama, Takashi Uchiyama, Shinji Miyoki and Yoshio Saito, Earth, Planets and Space 69, 77 (2017)
%




\bibitem{KAGRA} http://gwcenter.icrr.u-tokyo.ac.jp/en/


\bibitem{ioo:dt} S. Ueda, K Somiya et al., Class. Quantum Grav. 31 095003 (2014)
\bibitem{ioo:mzm} K Yamamoto et al., Class. Quantum Grav. 36 (2019) 205009.
\end{thebibliography}

